Model Checking Differentially Private Properties

### 2018-01-30 specifications.tex
small changes

As an example, for our threshold \lz{to do} model, we consider the property $\wedge_{i=1}^{7} \dpriv{3}{0}(\X^i \top) \wedge \PJ{\le .1}(\X^7 F T) \wedge \dpriv{3}{0}(\X^7 F \top)$.
that is used to express the privacy for our threshold Markov chains. It is only a valid formula if we would allow infinite conjunctions. However, it is interesting to note the relation to language equivalence for probabilistic automata\lz{to be discussed}

>>>>

As an example, for our threshold model(Algorithm ~\ref{algorithm:online-model}) , we consider the property $\wedge_{i=1}^{6} \dpriv{3}{0}(\X^i \top) \wedge \PJ{\le 0.025}(\X^6 F \top) \wedge \dpriv{3}{0.025}(\X^6 F \top)$, to express the privacy. The initial state of the corresponding Markov chain, where the input threshold $t$ is $3$, and the database $d$ is $4$, satisfies the above property by our computation. It means the probability of seeing $\top$  on any particular position, within $6$ steps, is $(3, 0)$-differentially private for the database $d$ and its neighbours($3$ and $5$). It also states that the probability of seeing $\top$ after no less than $6$ steps, is smaller than $0.025$ and is  $(3, 0.025)$-differentially private.
It is only a valid formula if we would allow infinite conjunctions. However, it is interesting to note the relation to language equivalence for probabilistic automata\lz{to be discussed}
